Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2016-11-13 code/rmarkdown/supporting_information.Rmd
+ fix supp info figures + tables + reorder si figures and tables + update si figures and table numbers in main tex

---
fontsize: 11pt
documentclass: article
bibliography: references.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
    includes:
      in_header: [preamble.tex, si-preamble.tex]
---
# Supporting Information
All data and code is stored in an online repository (\url{www.github.com/jeffreyhanson/genetic.surrogates}) to replicate analyses in this study. See the \textit{README} file for instructions.

@@

```{r, echo=FALSE, include=FALSE}
plot.spp.spaces <- function(i) {
  ## prepare data
  # get vector of adaptive and neutral column names
  adapt.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_adaptive_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  neutral.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_neutral_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  env.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_env_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  # skip species if not used in analysis
  curr.FPLY <- grid.FPLY[,
    c(adapt.col, neutral.col, env.col,
    'long','lat','group'),drop=FALSE]
  curr.FPLY <- curr.FPLY[which(!is.na(curr.FPLY[[1]])),]
  curr.FPLY <- curr.FPLY %>% gather(d, value, contains('adaptive'), contains('neutral'), contains('env')) %>%
    mutate(
      d=gsub(paste0(unique(spp.samples.DF$species)[i], '_'), '', d, fixed=TRUE),
      d=gsub('_', ' ', d, fixed=TRUE))
  for (j in seq_len(length(adapt.col)+length(neutral.col)+length(env.col)))
    curr.FPLY[['d']] <- gsub(as.character(j), paste0('(', j, ')'), curr.FPLY[['d']], fixed=TRUE)
  curr.FPLY <- curr.FPLY %>% mutate(d=factor(gsub(' d(', ' (', d, fixed=TRUE)))
  # make plot
  curr.GROBS <- llply(unique(curr.FPLY$d), function(x) {
    ggplot() +
      geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
        fill='grey85', color='grey70') +
      geom_polygon(data=filter(curr.FPLY, d==x), aes_string(x='long', y='lat', 
        group='group', fill='value'), color='grey10') +
      theme_classic() +
      theme(
        axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
        panel.border=element_rect(color='black', fill=NA, size=1),
        strip.background = element_rect(fill='grey20'), strip.text = element_text(color='white', size=20)
      ) +
      coord_cartesian(
        xlim=buffered.range(grid.FPLY$long, 0),
        ylim=buffered.range(grid.FPLY$lat, 0)
      ) +
      scale_fill_gradientn(name='',
        colors=brewer.pal(9, 'RdYlBu'),
        guide=guide_colorbar(ticks=element_line(color='black'),
          border=element_line(color='black'), barheight=unit(3.0, 'cm'))
      ) + facet_wrap(~d)
  })
  do.call(grid.arrange, append(curr.GROBS, list(ncol=3)))
  invisible()
}

@@

  n.plots <- 0 
  # count adaptive plot
  if (adapt.col %in% names(grid.FPLY))
    n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
  # count neutral plot
  if (neutral.col %in% names(grid.FPLY))
    n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
  # count env plot
  n.plots <- n.plots + env.col
  # exports
  if (n.plots >= 3) return((((n.plots-1) %/% 3)+1) * 2)
  return(1.85)
}

calc.fig.width <- function(i) {
  # init
  adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
  neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
  env.col <- grepl(paste0(unique(spp.samples.DF$species)[i], '_env_d'), names(grid.FPLY), fixed=TRUE) %>%
    sum()
  n.plots <- 0 
  # count adaptive plot
  if (adapt.col %in% names(grid.FPLY))
    n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
  # count neutral plot
  if (neutral.col %in% names(grid.FPLY))
    n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
  # count env plot
  n.plots <- n.plots + env.col
  # exports
  if (n.plots >= 3) return(10)
  return(4 * n.plots)
}

@@

```{r, echo=FALSE, fig.width=calc.fig.width(1), fig.height=calc.fig.height(1), fig.width=calc.fig.width(1), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (is.speciesPlottable(1)) plot.spp.spaces(1)
 ```

```{r, echo=FALSE, fig.width=calc.fig.width(2), fig.height=calc.fig.height(2), fig.width=calc.fig.width(2), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(2)) plot.spp.spaces(2)
```

```{r, echo=FALSE, fig.width=calc.fig.width(3), fig.height=calc.fig.height(3), fig.width=calc.fig.width(3), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(3)) plot.spp.spaces(3)
```

```{r, echo=FALSE, fig.width=calc.fig.width(4), fig.height=calc.fig.height(4), fig.width=calc.fig.width(4), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(4)) plot.spp.spaces(4)
```

```{r, echo=FALSE, fig.width=calc.fig.width(5), fig.height=calc.fig.height(5), fig.width=calc.fig.width(5), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(5)) plot.spp.spaces(5)
```

```{r, echo=FALSE, fig.width=calc.fig.width(6), fig.height=calc.fig.height(6), fig.width=calc.fig.width(6), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(6)) plot.spp.spaces(6)
```

```{r, echo=FALSE, fig.width=calc.fig.width(7), fig.height=calc.fig.height(7), fig.width=calc.fig.width(7), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(7)) plot.spp.spaces(7)
```

```{r, echo=FALSE, fig.width=calc.fig.width(8), fig.height=calc.fig.height(8), fig.width=calc.fig.width(8), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(8)) plot.spp.spaces(8)
```

```{r, echo=FALSE, fig.width=calc.fig.width(9), fig.height=calc.fig.height(9), fig.width=calc.fig.width(9), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(9)) plot.spp.spaces(9)
```

```{r, echo=FALSE, fig.width=calc.fig.width(10), fig.height=calc.fig.height(10), fig.width=calc.fig.width(10), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(10)) plot.spp.spaces(10)
```

```{r, echo=FALSE, fig.width=calc.fig.width(11), fig.height=calc.fig.height(11), fig.width=calc.fig.width(11), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(11)) plot.spp.spaces(11)
```

```{r, echo=FALSE, fig.width=calc.fig.width(12), fig.height=calc.fig.height(12), fig.width=calc.fig.width(12), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(12)) plot.spp.spaces(12)
```

```{r, echo=FALSE, fig.width=calc.fig.width(13), fig.height=calc.fig.height(13), fig.width=calc.fig.width(13), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(13)) plot.spp.spaces(13)
```

```{r, echo=FALSE, fig.width=calc.fig.width(14), fig.height=calc.fig.height(14), fig.width=calc.fig.width(14), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(14)) plot.spp.spaces(14)
```

```{r, echo=FALSE, fig.width=calc.fig.width(15), fig.height=calc.fig.height(15), fig.width=calc.fig.width(15), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(15)) plot.spp.spaces(15)
```

```{r, echo=FALSE, fig.width=calc.fig.width(16), fig.height=calc.fig.height(16), fig.width=calc.fig.width(16), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(16)) plot.spp.spaces(16)
```

```{r, echo=FALSE, fig.width=calc.fig.width(17), fig.height=calc.fig.height(17), fig.width=calc.fig.width(17), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(17)) plot.spp.spaces(17)
```

```{r, echo=FALSE, fig.width=calc.fig.width(18), fig.height=calc.fig.height(18), fig.width=calc.fig.width(18), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(18)) plot.spp.spaces(18)
```

```{r, echo=FALSE, fig.width=calc.fig.width(19), fig.height=calc.fig.height(19), fig.width=calc.fig.width(19), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(19)) plot.spp.spaces(19)
```

```{r, echo=FALSE, fig.width=calc.fig.width(20), fig.height=calc.fig.height(20), fig.width=calc.fig.width(20), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(20)) plot.spp.spaces(20)
```

```{r, echo=FALSE, fig.width=calc.fig.width(21), fig.height=calc.fig.height(21), fig.width=calc.fig.width(21), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(21)) plot.spp.spaces(21)
```

```{r, echo=FALSE, fig.width=calc.fig.width(22), fig.height=calc.fig.height(22), fig.width=calc.fig.width(22), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(22)) plot.spp.spaces(22)
```

```{r, echo=FALSE, fig.width=calc.fig.width(23), fig.height=calc.fig.height(23), fig.width=calc.fig.width(23), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(23)) plot.spp.spaces(23)
```

```{r, echo=FALSE, fig.width=calc.fig.width(24), fig.height=calc.fig.height(24), fig.width=calc.fig.width(24), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(24)) plot.spp.spaces(24)
```

```{r, echo=FALSE, fig.width=calc.fig.width(25), fig.height=calc.fig.height(25), fig.width=calc.fig.width(25), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(25)) plot.spp.spaces(25)
```

```{r, echo=FALSE, fig.width=calc.fig.width(26), fig.height=calc.fig.height(26), fig.width=calc.fig.width(26), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(26)) plot.spp.spaces(26)
```

```{r, echo=FALSE, fig.width=calc.fig.width(27), fig.height=calc.fig.height(27), fig.width=calc.fig.width(27), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(27)) plot.spp.spaces(27)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=calc.fig.height3(n_distinct(geo.surrogacy.DF$Species)), fig.cap='The relationship between the proportion of neutral genetic variation secured in a prioritizaiton and the proportion of geographic variation it also secures. Conventions are detailed in Figure S56.'}
# format data
curr.DF <- geo.surrogacy.DF %>% filter(!is.na(genetic.held)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2 <- geo.surrogate.spp.DF %>% filter(!is.na(r2CU)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2$R2_repr <- round(curr.DF2$r2CU,2)
curr.DF2$R2_repr <- sapply(curr.DF2$R2_repr, function(x) {as.character(as.expression(substitute(~~italic(R)^2~"="~r2, list(r2=x))))})
curr.DF2$surrogate.held <- 0
curr.DF2$genetic.held <- 0.9

@@

```{r, include=FALSE}
render_gvis <- function(x) {
  file = tempfile(fileext='.png')
  rsvg::rsvg_png(charToRaw(DiagrammeRsvg::export_svg(x)), file)
  grid::grid.raster(png::readPNG(file))
}
```

>>>>

---
fontsize: 11pt
documentclass: article
bibliography: references.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
    includes:
      in_header: [preamble.tex, si-preamble.tex]
---
# Supporting Information
All data and code is stored in an online repository (\url{www.github.com/jeffreyhanson/genetic-surrogates}) to replicate analyses in this study. See the \textit{README} file for instructions.

@@

```{r, echo=FALSE, include=FALSE}
plot.spp.spaces <- function(i) {
  ## prepare data
  # get vector of adaptive and neutral column names
  adapt.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_adaptive_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  neutral.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_neutral_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  env.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_env_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  # skip species if not used in analysis
  curr.FPLY <- grid.FPLY %>%
    select(one_of(adapt.col, neutral.col, env.col), group, long, lat) %>%
    mutate_each(funs(unname), one_of(adapt.col, neutral.col, env.col)) %>%
    filter(!is.na(.[[1]])) %>%
    gather(d, value, contains('adaptive'), contains('neutral'), contains('env')) %>%
    mutate(d=as.character(d)) %>%
    mutate(d=gsub(paste0(unique(spp.samples.DF$species)[i], '_'), '', d, fixed=TRUE)) %>%
    mutate(d=gsub('_', ' ', d, fixed=TRUE)) %>%
    mutate(d=gsub('env', 'environmental', d, fixed=TRUE))
  for (j in seq_len(max(length(adapt.col),length(neutral.col),length(env.col))))
    curr.FPLY$d <- gsub(paste0('d', as.character(j)), paste0('(', j, ')'), curr.FPLY$d, fixed=TRUE)
  # make plot
  curr.GROBS <- llply(unique(curr.FPLY$d), function(x) {
    ggplot() +
      geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
        fill='grey85', color='grey70') +
      geom_polygon(data=filter(curr.FPLY, d==x), aes_string(x='long', y='lat', 
        group='group', fill='value'), color='grey10') +
      theme_classic() +
      theme(
        axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
        panel.border=element_rect(color='black', fill=NA, size=1),
        strip.background = element_rect(fill='grey20'), strip.text = element_text(color='white', size=20)
      ) +
      coord_cartesian(
        xlim=buffered.range(grid.FPLY$long, 0),
        ylim=buffered.range(grid.FPLY$lat, 0)
      ) +
      scale_fill_gradientn(name='',
        colors=brewer.pal(9, 'RdYlBu'),
        guide=guide_colorbar(ticks=element_line(color='black'),
          border=element_line(color='black'), barheight=unit(3.0, 'cm')),
        labels=function(x) {formatC(x, format='f', digits=2)}
      ) + facet_wrap(~d)
  })
  do.call(grid.arrange, append(curr.GROBS, list(ncol=3)))
  invisible()
}

@@

  n.plots <- 0 
  # count adaptive plot
  if (adapt.col %in% names(grid.FPLY))
    n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
  # count neutral plot
  if (neutral.col %in% names(grid.FPLY))
    n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
  # count env plot
  n.plots <- n.plots + env.col
  # exports
  if (n.plots == 0) return(1)
  if (n.plots >= 3) return((((n.plots-1) %/% 3)+1) * 2)
  return(1.85)
}

calc.fig.width <- function(i) {
  # init
  adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
  neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
  env.col <- grepl(paste0(unique(spp.samples.DF$species)[i], '_env_d'), names(grid.FPLY), fixed=TRUE) %>%
    sum()
  n.plots <- 0 
  # count adaptive plot
  if (adapt.col %in% names(grid.FPLY))
    n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
  # count neutral plot
  if (neutral.col %in% names(grid.FPLY))
    n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
  # count env plot
  n.plots <- n.plots + env.col
  # exports
  if (n.plots == 0) return(1)
  if (n.plots >= 3) return(10)
  return(4 * n.plots)
}

@@

```{r, echo=FALSE, fig.width=calc.fig.width(1), fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. Each panel shows a different dimension of variation as indicated by its title. Squares represent planning units. Samples collected from the species were subject to NMDS to ordinate the main axes of adaptive (if detected) and neutral genetic variation. The bioclimatic data were clipped to planning units where the species was found, and subject to a principal components analysis to summarise the main gradients of environmental variation. The panels show the spatial distribution of the ordinated environmental and genetic data averaged to the planning-unit level. Planning units where individuals were not observed are shown in gray.')}
if (is.speciesPlottable(1)) plot.spp.spaces(1)
```

```{r, echo=FALSE, fig.width=calc.fig.width(2), fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(2)) plot.spp.spaces(2)
```

```{r, echo=FALSE, fig.width=calc.fig.width(3), fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(3)) plot.spp.spaces(3)
```

```{r, echo=FALSE, fig.width=calc.fig.width(4), fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(4)) plot.spp.spaces(4)
```

```{r, echo=FALSE, fig.width=calc.fig.width(5), fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(5)) plot.spp.spaces(5)
```

```{r, echo=FALSE, fig.width=calc.fig.width(6), fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(6)) plot.spp.spaces(6)
```

```{r, echo=FALSE, fig.width=calc.fig.width(7), fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(7)) plot.spp.spaces(7)
```

```{r, echo=FALSE, fig.width=calc.fig.width(8), fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(8)) plot.spp.spaces(8)
```

```{r, echo=FALSE, fig.width=calc.fig.width(9), fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(9)) plot.spp.spaces(9)
```

```{r, echo=FALSE, fig.width=calc.fig.width(10), fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(10)) plot.spp.spaces(10)
```

```{r, echo=FALSE, fig.width=calc.fig.width(11), fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(11)) plot.spp.spaces(11)
```

```{r, echo=FALSE, fig.width=calc.fig.width(12), fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(12)) plot.spp.spaces(12)
```

```{r, echo=FALSE, fig.width=calc.fig.width(13), fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(13)) plot.spp.spaces(13)
```

```{r, echo=FALSE, fig.width=calc.fig.width(14), fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(14)) plot.spp.spaces(14)
```

```{r, echo=FALSE, fig.width=calc.fig.width(15), fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(15)) plot.spp.spaces(15)
```

```{r, echo=FALSE, fig.width=calc.fig.width(16), fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(16)) plot.spp.spaces(16)
```

```{r, echo=FALSE, fig.width=calc.fig.width(17), fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(17)) plot.spp.spaces(17)
```

```{r, echo=FALSE, fig.width=calc.fig.width(18), fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(18)) plot.spp.spaces(18)
```

```{r, echo=FALSE, fig.width=calc.fig.width(19), fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(19)) plot.spp.spaces(19)
```

```{r, echo=FALSE, fig.width=calc.fig.width(20), fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(20)) plot.spp.spaces(20)
```

```{r, echo=FALSE, fig.width=calc.fig.width(21), fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(21)) plot.spp.spaces(21)
```

```{r, echo=FALSE, fig.width=calc.fig.width(22), fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(22)) plot.spp.spaces(22)
```

```{r, echo=FALSE, fig.width=calc.fig.width(23), fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(23)) plot.spp.spaces(23)
```

```{r, echo=FALSE, fig.width=calc.fig.width(24), fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(24)) plot.spp.spaces(24)
```

```{r, echo=FALSE, fig.width=calc.fig.width(25), fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(25)) plot.spp.spaces(25)
```

```{r, echo=FALSE, fig.width=calc.fig.width(26), fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(26)) plot.spp.spaces(26)
```

```{r, echo=FALSE, fig.width=calc.fig.width(27), fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(27)) plot.spp.spaces(27)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=calc.fig.height3(n_distinct(geo.surrogacy.DF$Species)), fig.cap='The relationship between the proportion of neutral genetic variation secured in a prioritizaiton and the proportion of geographic variation it also secures. Conventions are detailed in Figure S28.'}
# format data
curr.DF <- geo.surrogacy.DF %>% filter(!is.na(genetic.held)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2 <- geo.surrogate.spp.DF %>% filter(!is.na(r2CU)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2$R2_repr <- round(curr.DF2$r2CU,2)
curr.DF2$R2_repr <- sapply(curr.DF2$R2_repr, function(x) {as.character(as.expression(substitute(~~italic(R)^2~"="~r2, list(r2=x))))})
curr.DF2$surrogate.held <- 0
curr.DF2$genetic.held <- 0.9

@@

```{r, include=FALSE}
render_gvis <- function(x) {
  file = tempfile(fileext='.png')
  rsvg::rsvg_png(charToRaw(DiagrammeRsvg::export_svg(DiagrammeR::grViz(x))), file)
  grid::grid.raster(png::readPNG(file))
}
```
